The effects of binarity on planet occurrence rates measured by transit surveys

### 2017-12-14 paper/simplest_effects.tex
add footnote addressing planet radius scaling Q
paper: update volume visualization and caption

The single stars have luminosity $L_1$, and the twin binaries have luminosity 
$2L_1$.
Thus the twin binaries are selected out to a distance $\sqrt{2}$ times 
that of single stars.
This is a bad move, because the transit signal for any planet in a 
twin binary will be diluted by a factor of two:
\begin{equation}
\frac{{\rm signal}}{{\rm noise}}
\propto \frac{\mathcal{D} (r/R)^2}{F^{-1/2}}
\propto \mathcal{D} F^{1/2}
\propto \mathcal{D} L_{\rm sys}^{1/2} d^{-1}, \quad ({\rm true})
\end{equation}
where the dilution is $\mathcal{D} \equiv L_{\rm host}/L_{\rm sys}$, for 
$L_{\rm host}$ the the planet host's luminosity.
This means that the true maximum searchable distance for binaries, $d_{\rm 
det}$, is $1/\sqrt{2}$ times that of single stars.
The situation is illustrated in Fig.~\ref{fig:model_1_volumes}: only one in 
eight selected stars in binaries are truly searchable.

\begin{figure}[!tb]
    \begin{center}
        \includegraphics[width=0.6\textwidth]{figures/visualize_volumes.pdf}
    \end{center}
    \caption{
        Cartoon of the different selected and searchable volumes for single 
        stars (left column), and twin binaries (right column).
        This model (\#1) assumes all stars have equal mass and luminosity.
        Since the observer does not recognize the brighter binaries, they 
        select 
        them out to a larger distance, $\sqrt{2}\times$ that of single stars.
        However, dilution causes the twin binaries to only be searchable in 
        one 
        eighth of their selected volume.
    }
    \label{fig:model_1_volumes}
\end{figure}

>>>>

The single stars have luminosity $L_1$, and the twin binaries have luminosity 
$2L_1$.
Thus the twin binaries are selected out to a distance $\sqrt{2}$ times 
that of single stars.
This is a bad move, because the transit signal for any planet in a 
twin binary will be diluted by a factor of two:
\begin{equation}
\frac{{\rm signal}}{{\rm noise}}
\propto \frac{\mathcal{D} (r/R)^2}{F^{-1/2}}
\propto \mathcal{D} F^{1/2}
\propto \mathcal{D} L_{\rm sys}^{1/2} d^{-1}, \quad ({\rm true})
\label{eq:snr_true}
\end{equation}
where the dilution is $\mathcal{D} \equiv L_{\rm host}/L_{\rm sys}$, for 
$L_{\rm host}$ the the planet host's luminosity.
This means that the true maximum searchable distance for binaries, $d_{\rm 
det}$, is $1/\sqrt{2}$ times that of single stars.
The situation is illustrated in Fig.~\ref{fig:model_1_volumes}: only one in 
eight selected stars in binaries are truly searchable.

\begin{figure}[!tb]
    \begin{center}
        \includegraphics[width=0.6\textwidth]{figures/visualize_volumes.pdf}
    \end{center}
    \caption{
        Cartoon of the searchable volumes for single stars ({\it left}), and 
        twin binaries ({\it right}).
        This model (\#1) assumes all stars have equal mass and luminosity, and 
        all planets have the same true radius $r=r_p$.
        {\it Top:} At an apparent radius $r\a=r_p$,
        the observer selects twin binaries out to a larger         
        distance, $\sqrt{2}\times$ that of single stars.
        Because of dilution, there are no planets in twin binaries with 
        $r\a=r_p$.
        {\it Middle:} At an apparent radius $r\a=r_p/\sqrt{2}$, the 
        searched volumes are half those at $r\a=r_p$. 
        The only detected planets with $r\a=r_p/\sqrt{2}$ orbit twin binaries.
        {\it Bottom:} Planets with a true radius $r=r_p$ are searchable to 
        a maximum distance $d_0$ around singles, and $d_0/\sqrt{2}$ around 
        twin binaries. These distances are the same as what an observer 
        selects based on apparent radii.
    }
    \label{fig:model_1_volumes}
\end{figure}
